The Two Dualities of Computation: Negative and Fractional Types

### 2012-03-09 rational.tex
error
mult constructions
_

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Rational Types}
\label{sec:rat}

@@

{{-(b1 + b2) <-> (b1) + (-b2)}}

@@

>>>>

\roshan{Say somewhere that {{langRev}} corresponds to computing in the
  commutative rig of whole numbers. More bluntly {{langRev}} is whole
  numbers with addition and multiplication, while {{langRevEE}} is the
  rational with addition and multiplication.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Computing in the Field of Rationals : {{langRevEE}} }
\label{sec:rat}

@@

{{-(b1 + b2) <-> (-b1) + (-b2)}}

@@

\paragraph*{Distributing fractions over {{*}} }

{{1/(b1*b2) <-> (1/b1) * (1/b2)}}

\paragraph*{Multiplying Fractions}

{{b1/b2 * b3/b4 <-> (b1*b3)/(b2*b4)}}

\paragraph*{Lifting Computation intro fractions}

{{b1 <-> b2 ==> 1/b1 <-> 1/b2}}

\paragraph*{Adding the numerator}

{{b1/b + b2/b <-> (b1+b2)/b}}

\paragraph*{Fraction Addition}

{{b1/b2 + b3/b4 <-> (b1*b4+b3*b2)/(b2*b4) }}
